

\section{Useful formulae}

\subsection{12d Gravity}
Written in Einstein frame, and real torus coordinates, with convention $(p,q)$ denoting (NSNS, RR) charges, the 12d F-theory metric is
\begin{equation}
\hat{g}_{MN}
= \begin{pmatrix}
    g_{mn} & 0 \\
    0 & \hat{g}_{ab}
\end{pmatrix},\quad
\hat{g}_{ab}
= \frac{1}{\tau_2}
\begin{pmatrix}
    1 & \tau_1 \\
    \tau_1 & |\tau|^2    
\end{pmatrix}
\end{equation}
From this 12d metric, one finds that the nonvanishing Christoffel symbols are $\hat{\Gamma}^p{}_{mn} = \Gamma^p{}_{mn}$, $\hat{\Gamma}^a{}_{bm} = \frac{1}{2}g^{ac}g_{bc,m}$, $\hat{\Gamma}^m{}_{ab} = - \frac{1}{2}g^{mp}g_{ab,p}$.
With $a$ indexing rows and $b$ columns:
\begin{equation}
\begin{aligned}
\Gamma^a{}_{bm}
&=\frac{1}{2 \tau_2^2}\begin{pmatrix}
    -\tfrac12 \nabla_m|\tau|^2 & |\tau|^2\nabla_m\tau_1 - \tau_1 \nabla_m|\tau|^2 \\
    \nabla_m\tau_1 & \tfrac12 \nabla_m|\tau|^2
\end{pmatrix}\\
\Gamma_{abm}=-\Gamma^m{}_{ab}
&= \frac{1}{2\tau_2}\begin{pmatrix}
    -\nabla_m\ln\tau_2
    & \nabla_m\tau_1 - \tau_1\nabla_m\ln\tau_2 \\
    \nabla_m\tau_1 - \tau_1\nabla_m\ln\tau_2 & \nabla_m|\tau|^2 - |\tau|^2\nabla_m\ln\tau_2
\end{pmatrix}
=\frac{1}{2}g_{ab,m}
\end{aligned}
\end{equation}
The components of $R_{ambn}$ are given by

\medskip
\renewcommand{\arraystretch}{1.8}
\begin{tabular}{c|cccccc}
\toprule
$R_{ambn}$ 
  & $\nabla_m\nabla_n\tau_1$ 
  & $\nabla_m\nabla_n\tau_2$ 
  & $(\nabla_m\tau_1)(\nabla_n\tau_1)$ 
  & $\nabla_m\tau_1\nabla_n\tau_2$ 
  & $\nabla_m\tau_2\nabla_n\tau_1$ 
  & $(\nabla_m\tau_2)(\nabla_n\tau_2)$ \\
\midrule
$R_{1m1n}$ & $0$ & $\frac{1}{2\tau_2^2}$ & $\frac{1}{4\tau_2^3}$ & $0$ & $0$ & $-\frac{3}{4\tau_2^3}$ \\
$R_{1m2n}$ & $-\frac{1}{2\tau_2}$ & $\frac{\tau_1}{2\tau_2^2}$ & $\frac{\tau_1}{4\tau_2^3}$ & $\frac{1}{4\tau_2^2}$ & $\frac{3}{4\tau_2^2}$ & $-\frac{3\tau_1}{4\tau_2^3}$ \\
$R_{2m1n}$ & $-\frac{1}{2\tau_2}$ & $\frac{\tau_1}{2\tau_2^2}$ & $\frac{\tau_1}{4\tau_2^3}$ & $\frac{3}{4\tau_2^2}$ & $\frac{1}{4\tau_2^2}$ & $-\frac{3\tau_1}{4\tau_2^3}$ \\
$R_{2m2n}$ & $-\frac{\tau_1}{\tau_2}$ & $\frac{\tau_1^2-\tau_2^2}{2\tau_2^2}$ & $\frac{\tau_1^2-3\tau_2^2}{4\tau_2^3}$ & $\frac{\tau_1}{\tau_2^2}$ & $\frac{\tau_1}{\tau_2^2}$ & $\frac{\tau_2^2-3\tau_1^2}{4\tau_2^3}$ \\
\bottomrule
\end{tabular}
\medskip

As for the rest of the non-vanishing Riemann tensor components, we have
\begin{equation}
\begin{aligned}
R_{mn12} 
&= R_{1m2n} - R_{2m1n}
= \frac{1}{2\tau_2^2}[\nabla_m\tau_2\nabla_n\tau_1-\nabla_m\tau_1\nabla_n\tau_2]\\
R_{1212}
&= -\frac{1}{2}g^{mn}g^{ab} R_{ambn} = \frac{1}{4\tau_2^2}|\nabla \tau|^2
\end{aligned}
\end{equation}

It follows that $R_{mnab}R_{rs}{}^{ab} = (g^{ac}g^{bd}-g^{ad}g^{bc}) R_{ambn} R_{crds}$, and $R_{abcd}R^{abcd} = \tfrac14 R^{am}{}_{am} R^{bn}{}_{bn}$.

We list some further identities:
\begin{enumerate}
    \item $R_{ambm} R_{bnan} = R_{ambm} R_{anbn}$,
\end{enumerate}

We note that generically $R_{ambn}$, $R_{1212}$ and $R_{mn12}$ are independent of each other.
The 12d Riemann tensors only provide 4 independent degrees of freedom for second order derivatives of $\tau$, while in total there are 6 independent degrees of freedom for second order derivatives of $\tau$, as given in the columns of the above table.
This is due to the specific metric ansatze adopted.
A direct consequence of such lack of independent Riemann tensors is that while we can write $|\nabla \tau|^2$ using 12d Riemann tensor, we can not do so for $(\nabla \tau_1)^2 - (\nabla \tau_2)^2$, which appears in 5-point 8-derivative 3-scalar type IIB effective actions in the form $\text{Re} P_m P^m$. This is a new fundamental obstruction to uplifting type IIB effective actions, not previously discussed in the literature.

\subsection{Complex Coordinates}
Alternatively, it is convenient to work with complex tangent-frame coordinates $z,\bar{z}$, as is commonly done in the literature.
This is in fact more compatible with how the $U(1)$ structure is conventionally presented in the literature.In such coordinates, the tangent frame metric takes the form $g_{zz} = g_{\bar{z}\bar{z}} = 0, g_{z\bar{z}} = \tfrac12$.
The Riemann tensor components are given by
\begin{equation}
R_{z\bar{z}z\bar{z}} = -\frac14 |P|^2,\quad
R_{mnz\bar{z}} = P_{[m}\bar{P}_{n]},\quad
R_{mzn\bar{z}} = - \frac{P_m \bar{P}_n}{2}\quad
R_{mznz} = \frac{D_m P_n}{2}.
\end{equation}
We note again, that as similar to the computation in real coordinates, the generically independent components of the Riemann tensors are not independent here. For example, we can obtain $R_{z\bar{z}z\bar{z}}$ by contracting $R_{mzn\bar{z}}$. 
This results in an underparameterization of second order derivatives on $\tau$ in 10d using 12d Riemann tensors.
One can see that while we are able to write $\bar{P}_m P_n$ with 12d Riemann tensor, we can not do so for $P_m P_n$. 

\subsection{IIB useful equations}

Reference: \cite{Policastro:2008hg,Minasian:2015bxa}

The rank-4 tensor $DP$ is defined by
\begin{equation}
(\nabla \mathcal{P})_{mn}{}^{pq} \equiv 
\delta_{[m}^{[p} \nabla_{n]}\mathcal{P}^{q]}
\end{equation}
which has the same symmetries as the Riemann tensor.
The $U(1)$ connection and one-form are defined by
\begin{equation}
Q_m =-\frac{\nabla_m\tau_1}{2\tau_2},\quad
P_m = \frac{i}{2\tau_2} \nabla_m \tau,
\end{equation}
From here one can compute
\begin{equation}
\begin{aligned}
D_m \mathcal{P}_n
&= \nabla_m \mathcal{P}_n - 2i Q_m \mathcal{P}_n
&= 2\mathcal{P}_m \mathcal{P}_n + \frac{i}{2\tau_2} \nabla_m \nabla_n \tau \\
D_m \bar{\mathcal{P}}_n
&= \nabla_m \bar{\mathcal{P}}_n + 2i Q_m \bar{\mathcal{P}}_n
&= 2\bar{\mathcal{P}}_m \bar{\mathcal{P}}_n - \frac{i}{2\tau_2} \nabla_m \nabla_n \bar{\tau}
\end{aligned}
\end{equation}
which implies that $D_m P_n$ is symmetric.
The complex 3-form is defined by
\begin{equation}
G_3 \equiv \frac{1}{\sqrt{\tau_2}} (F_3 - \tau H_3)
\end{equation}

\subsection{Type IIB terms viewed in 12d}
Here we lay out the dictionary for translating 10d type IIB effective action terms into 12d geometric objects. We will work with real coordinates $y_1, y_2$.

One can show that
\begin{equation}
\bar{P}_m P_n = \frac{1}{2} \hat{g}^{ab} R_{ambn} - \frac{i}{2} R_{mn12}
\end{equation}
which implies $2|P|^2 = g^{mn}\hat{g}^{ab} R_{ambn} = \hat{R} - R$.

Similarily, one can show that
\begin{equation}
D_m P_n = -\tau_2 R_{1m1n} + \tfrac{1}{2} g^{ab} R_{ambn} + i \left( \tau_1  R_{1m1n} - \tfrac{1}{2}(R_{1m2n} + R_{2m1n}) \right)
\end{equation}

On the other hand, $P_m$ itself while can be written with 12d Christoffel symbols, which indeed become 10d tensors upon compactification, can not be written as a linear combination of 12d Riemann tensors.
This means we also can not write terms as $PP$ and $\bar{P}\bar{P}$, which appear at 5-point type IIB amplitudes, using Riemann tensors.

\begin{equation}
\begin{aligned}
D_m\bar{P}_n D_r P_s &= \frac{1}{4}(g^{ac}g^{bd} - g^{ab}g^{cd}+g^{ad}g^{bc})R_{ambn}R_{crds}\\
D_m \bar{G}_{3,nrs} D_{m'} G_{3,n'r's'}
&= \hat{\nabla}_m F_{4,nrs a} \hat{\nabla}_{m'} F_{4,n'r's' b} g^{ab}\end{aligned}
\end{equation}

We also have that 

$$|DG_3|^2 = (\hat{\nabla} F_4)_a (\hat{\nabla} F_4)^a$$

as well as

\begin{equation}
\text{Re} D_m P_n D_r \bar{G}_3 D_s \bar{G}_3 = \frac{1}{2} (g^{ac} g^{bd} - g^{ab}g^{cd} + g^{ad}g^{bc}) R_{ambn} \nabla_r F_{4c} \nabla_s F_{4d}
\end{equation}


\subsection{Tensor Identities}
In generic dimensions, one has that
\begin{equation}
\begin{aligned}
\epsilon_{\mu_1...\mu_D} 
&= \sqrt{|g|}\varepsilon_{\mu_1...\mu_D},\\
\varepsilon_{0,1,...,(D-2),(D-1)} 
&= 1,\\
\epsilon_{\mu_1...\mu_p \lambda_1 ...\lambda_{D-p}}
\epsilon^{\nu_1...\nu_p \lambda_1 ...\lambda_{D-p}}
&=(-1)^{[t]} p!(D-p)!\delta^{\nu_1...\nu_p}_{\mu_1...\mu_p}
\end{aligned}
\end{equation}
So that on an Euclidean 2-torus, we have that $\epsilon^{ac}\epsilon^{bd} = g^{ab}g^{cd} - g^{ad}g^{bc}$.

The contraction of the $t_8 t_8$ tensor with four rank-4 tensors is defined by
\begin{align}
	t_8 t_8 \left\{ ABCD \right\} := (t_8)^{a_1 \ldots a_8} (t_8)^{b_1 \ldots b_8} A_{a_1 a_2 b_1 b_2} B_{a_3 a_4 b_3 b_4} C_{a_5 a_6 b_5 b_6} D_{a_7 a_8 b_7 b_8} \,,
\end{align}
The $t_8$ tensor itself is conventionally \cite{Aggarwal:2025lxf,Liu:2025uqu} defined to represent taking traces with cyclic symmetry:
\begin{equation}
t_8 ABCD = 8 \text{tr} (ABCD) - 2 \text{tr} (AB) \text{tr} (CD) + \text{cycl}(B,C,D).
\end{equation}
It also has a component definition \footnote{See also \cite{Minasian:2015bxa}}
\begin{equation}
\begin{aligned}
t_8^{a_1 a_2 b_1 b_2 c_1 c_2 d_1 d_2}
&= 8 g^{a_2 b_1} g^{b_2 c_1} g^{c_2 d_1} g^{d_2 a_1}
- 2 g^{a_2 b_1} g^{b_2 a_1} g^{c_2 d_1} g^{d_2 c_1}\\
&+ \text{cycl}(b,c,d)
- (a_1 \leftrightarrow a_2)
- (b_1 \leftrightarrow b_2)
- (c_1 \leftrightarrow c_2)
- (d_1 \leftrightarrow d_2).
\end{aligned}
\end{equation}
In particular, when acting on a tensor with the symmetries of the Riemann tensor, we have
\begin{equation}
\begin{aligned}
t_8 t_8 R^4 &= 3 \times 2^7 \Biggl\{
R_{mnrs} R^{sp}{}_{qu} R^{umvr} R_{pv}{}^{nq}
+ \frac{1}{2} R_{mnrs} R^{spnq} R_{qupv} R^{vrum} \notag \\
&\quad - \frac{1}{2} R_{mnrs} R^{rsnp} R_{pquv} R^{qmuv}
- \frac{1}{4} R_{mnrs} R^{rs}{}_{pq} R^{qmuv} R_{uv}{}^{np} \notag \\
&\quad + \frac{1}{16} R_{mnrs} R^{mnpq} R_{pquv} R^{uvrs}
+ \frac{1}{32} (R_{mnrs} R^{mnrs})^2
\Biggr\}. \label{eq:A2}
\end{aligned}
\end{equation}
Another useful identity is if $S$ has Riemann-like symmetries, then
\begin{equation}
\begin{aligned}
t_8 t_8 R^2 S^2 &=
{}4\,R^{m n r s} R_{m n r s} S^{t u v w} S_{t u v w}+16\,R^{m n r s} R_{m n}\,^{t u} S_{r s}\,^{v w} S_{t u v w}\\
&-64\,R^{m n r s} R_{m n r}\,^{t} S_{s}\,^{u v w} S_{t u v w}-32\,R^{m n r s} R_{m n}\,^{t u} S_{r t}\,^{v w} S_{s u v w}\\
&+8\,R^{m n r s} R^{t u v w} S_{m n r s} S_{t u v w}+8\,R^{m n r s} R^{t u v w} S_{m n t u} S_{r s v w}\\
&-64\,R^{m n r s} R_{m}\,^{t u v} S_{n}\,^{w}\,_{u v} S_{r s t w}-64\,R^{m n r s} R_{m}\,^{t u v} S_{n}\,^{w}\,_{r s} S_{t w u v}\\
&-64\,R^{m n r s} R^{t u v w} S_{m n r t} S_{s u v w}+128\,R^{m n r s} R_{m}\,^{t}\,_{r}\,^{u} S_{n}\,^{v}\,_{s}\,^{w} S_{t v u w}\\
&+128\,R^{m n r s} R_{m}\,^{t}\,_{r}\,^{u} S_{n}\,^{v}\,_{u}\,^{w} S_{s w t v}+256\,R^{m n r s} R_{m}\,^{t u v} S_{n}\,^{w}\,_{r u} S_{s v t w}\\
&+64\,R^{m n r s} R^{t u v w} S_{m t r v} S_{n u s w}
\label{eq:t8R2S2}
\end{aligned}
\end{equation}

\subsection{Additional tensor identities}
Define $K^{mnrs} \equiv D^m\bar{P}^n D^r P^s$.
For any contraction with a real tensor $T$, one has the effective symmetry
\begin{equation}
    \mathcal{K}^{mnrs} \;\cong\; \mathcal{K}^{rsmn}.
\end{equation}
Proof is done by conjugation.
It follows that
\begin{equation}\label{eq:K_vanish}
    \mathcal{K}^{mnrs}R_{m}{}^{t}{}_{n}{}^{u}\,R_{rtsu} = 0.
\end{equation}
\emph{Proof.}
Apply the first Bianchi identity $R_{r[tsu]}=0$ to the second Riemann factor. \(\square\)

Furthermore,
\begin{equation}\label{eq:K_bianchi}
    \mathcal{K}^{mnrs}\,R_{mr}{}^{tu}\,R_{nstu}
    = 2\,\mathcal{K}^{mnrs}\,R_{m}{}^{t}{}_{r}{}^{u}\,R_{nstu}.
\end{equation}
\emph{Proof.}
First Bianchi identity. \(\square\)
