\section{Introduction}
We begin by reviewing the known relations between type IIB and 12d, using a somewhat more general ``bottom-up" approach.
The type IIB axio-dilaton action, at the two-derivative level, can be written as
\begin{equation}
2\kappa^2 S_{IIB,\tau}
= \int d^{10}x \sqrt{-g} \left(R - 2 P_m \overline{P}^m\right).
\label{eq:IIB-two-derivative}
\end{equation}
where $P_m \equiv \frac{i\nabla_m \tau}{2\tau_2}$, and $\tau = \tau_1 + i \tau_2 = C_0 + i e^{-\Phi}$ is the axio-dilaton.

The proposal of F-theory \cite{Vafa:1996xn} is that for backreacted 7-brane configurations, the axio-dilaton profile $\tau$ can be geometrized as the complex structure of an auxiliary torus.
This proposal can be understood by noting that the 10d axio-dilaton action can be obtained by certain 12d action on a specific metric ansatze, where the 12d metric is given by
\begin{equation}
\widehat{g}_{MN}=\begin{pmatrix}
g_{mn} & 0 \\
0 &\widehat{g}_{ab}
\end{pmatrix},\quad
\widehat{g}_{ab}
=\frac{1}{\tau_2}\begin{pmatrix}
1& \tau_1\\
\tau_1 & \tau_1^2+\tau_2^2
\end{pmatrix}.
\label{eq:F-theory-ansatze}
\end{equation}
One may adopt complex tangent frame coordinates $z, \overline{z}$, with vielbein $e_{\alpha}{}^a = \frac{1}{2\sqrt{\tau_2}}\begin{pmatrix}
    -\tau & 1 \\ -\overline{\tau} & 1
\end{pmatrix}$, the nonvanishing components of the 12d Riemann tensor are \cite{Liu:2025uqu}
\begin{equation}
\widehat{R}_{mrns} = R_{mrns},\quad
R_{z\overline{z}z\overline{z}} = -\frac14 |P|^2,\quad
R_{mnz\overline{z}} = P_{[m}\overline{P}_{n]},\quad
R_{mzn\overline{z}} = - \frac{P_m \overline{P}_n}{2}\quad
R_{mznz} = \frac{D_m P_n}{2}.
\label{eq:12d-Riemann-complex}
\end{equation}
Substituting $P_m\overline{P}_n$ in \eqref{eq:IIB-two-derivative} with $R_{mzn\overline{z}}$, we find
\begin{equation}
\sqrt{-g}[R - 2 P_m \overline{P}^m]
=\sqrt{-\widehat{g}}[R + \widehat{R}^{mz}{}_{mz} + \widehat{R}^{m\overline{z}}{}_{m\overline{z}}]
=\sqrt{-\widehat{g}} \widehat{R},
\label{eq:2-derivative-index-splitting}
\end{equation}
which verifies that the F-theory ansatze \eqref{eq:F-theory-ansatze} relates the 10d axio-dilaton action to a 12d Einstein-Hilbert term.
Hence we may map solutions of 12d Einstein gravity, such as the pp-wave \cite{Tseytlin:1996ne} and the KK-monopole \cite{Cheng:2025efp} solutions, to type IIB geometries with nontrivial axio-dilaton profile.

What we have been discussing is the classical, two-derivative, two field type IIB theory, which is the leading term in the $\alpha'$ expansion of the type IIB string theory.
Under quantum corrections, \eqref{eq:IIB-two-derivative} receives higher order and higher derivative corrections, which can be computed from string perturbtion theory and non-perturbative saddles.
It is natural to ask whether such corrections can also be understood from 12d perspective, e.g. at 8-derivatives?
The answer does not appears to be a clearcut yes or no, the purpose of this writeup is to discuss the subtleties that arise.

\section{Type IIB at 4 points}

The 4-point 8-derivative effective action can be written \cite{Liu:2025uqu,Minasian:2015bxa,Policastro:2008hg} as
\begin{equation}
\begin{aligned}
\frac{L_{\text{4-pt}}}{\alpha\, f_{0}(\tau,\overline{\tau})}
&= t_{8}t_{8} \biggl[R^4+6R^{2}\left(4|\delta\nabla P|^{2}+|\nabla G_{3}|^{2}\right)+24|\delta \nabla P|^{2}|\nabla G_{3}|^{2}\\
&+12R\left(\delta \nabla P(\nabla\overline{G}_{3})^{2}+D\overline{P}(\nabla{G}_{3})^{2}\right)\biggr]\\
&+1536 |\nabla_m P_n \nabla^m P^n|^2\\
&+O_{2}\left((|\nabla G_{3}|^{2})^{2}\right)
\label{eq:PTaction}
\end{aligned}
\end{equation}
where $\alpha = \frac{(\alpha')^3}{3 \cdot 2^{12}}$ and $(\delta \nabla P)_{mrns} \equiv g_{[m[n} \nabla_{r]} P_{s]}$ is defined to have the same symmetries as the Riemann tensor, upto $\delta$-functions located at the sources of $\tau$.
Restricting to the gravity + scalar sector of \eqref{eq:PTaction}, we have
\begin{equation}
\frac{L_{\text{4-pt},\tau}}{\alpha f_0(\tau,\overline{\tau})} = t_8t_8
(R^4 + 24 R^2 |\delta \nabla P|^2) + 1536 (\nabla_m P_n \nabla^m P^n)(\nabla_r \overline{P}_s \nabla^r \overline{P}^s).
\label{eq:4pt-gravity-axiodilaton}
\end{equation}
In the 12d perspective $\tau$ is embedded in the metric.
Suppose certain axio-dilaton couplings in the 10d effective action admits a 12d interpretation, one shall be able to rewrite such terms using 12d-covariant differential operators acting on the metric, i.e. the 12d Riemann tensor \eqref{eq:12d-Riemann-complex}. 
Once we had replaced the 10d fields and their derivatives with their 12d counterparts, we may reexamine the resulting expression, and see if the terms group into a natuaral pattern as a result of index splitting.
We had carried out this exercise at the two-derivative level in \eqref{eq:2-derivative-index-splitting}, we now perform the same exercise at the 8-derivative level to \eqref{eq:4pt-gravity-axiodilaton}, as a way to review the results of \cite{Minasian:2015bxa}.

Let us begin by expanding the $t_8t_8$ contractions.
The $t_8t_8R^4$ contraction is known \cite{Policastro:2008hg} to be 
\begin{equation}
\begin{aligned}
\frac{t_8t_8 R^4}{3 \cdot 2^7}
&=  R_{pnqm} R^{prqs} R^{mt}{}_{ru} R^{nu}{}_{st} + \frac{1}{2}R_{mpnq} R^{qrps} R_{tsur} R^{untm} \\
& - \frac{1}{2}R_{mnrs} R^{rsnp} R_{pquv} R^{qmuv} - \frac{1}{4} R_{mnrs} R^{rs}{}_{pq} R^{qmuv} R^{np}{}_{uv}\\
& + \frac{1}{16} R_{mnrs} R^{mnpq} R_{pquv} R^{uvrs} + \frac{1}{32}(R_{mnrs} R^{mnrs})^2.
\end{aligned}
\label{eq:t8t8R4}
\end{equation}

Expanding the $t_8 t_8 R^2 |\delta \nabla P|^2$ sector, we find\footnote{
The computation is done with Cadabra, which agrees with the results of \cite{Minasian:2015bxa}. We have taken $f_0(\tau,\overline{\tau})$ to be $2\zeta(3) \tau_2^{3/2}$.
}
\begin{equation}
\begin{aligned}
\frac{1}{3 \cdot 2^{8}\zeta(3) \tau_2^{3/2}}\frac{L_{\text{4-pt},\tau}}{\alpha}
&=  \frac{t_8 t_8 R^4}{3 \cdot 2^7}
+ 4 \nabla_n P_m \nabla^r \overline{P}^s R^{mt}{}_{ru} R^{nu}{}_{st} \\
&+ 4 \nabla_m P_n \nabla^r \overline{P}^s R_{tsur} R^{untm}
+ 4 |\nabla_m P_n \nabla^m P^n|^2 \\
&- 4 \nabla_m P_n \nabla^n \overline{P}^r R_{rsuv} r^{smuv}
+ \frac{1}{2} \nabla_{m} P_{n} \nabla^{m}\overline{P}^{n}R^{rstu}R_{rstu} + O(R^2 P^3).
\end{aligned}
\end{equation}

The next step is to replace the 10d terms with their 12d counterparts. The only 10d terms that remains are $\nabla P$.
we note that because the only 12d Riemann tensor linear in $P$ is $R_{mznz}$ and its conjugate, so we have
\begin{equation}
\widehat{R}_{ambn} \widehat{R}^{a}{}_{r}{}^{b}{}_{s} = 2 \text{Re} D_m P_n D_r \overline{P}_s + O(P^3).
\end{equation}
Substituting this as well as $t_8 t_8 R^4$, we find
\begin{equation}
\begin{aligned}
\frac{1}{3 \cdot 2^{8}\zeta(3) \tau_2^{3/2}}\frac{L_{\text{4-pt},\tau}}{\alpha}
&=
R_{pnqm} R^{prqs} R^{mt}{}_{ru} R^{nu}{}_{st}
+ 2 \widehat{R}_{anbm} \widehat{R}^{arbs} R^{mt}{}_{ru} R^{nu}{}_{st}\\
& + \frac{1}{2}\left[ R_{mpnq} R^{qrps} R_{tsur} R^{untm}
+ 4 \widehat{R}_{ambn} \widehat{R}^{bras} R_{tsur} R^{untm}
+ 2 \widehat{R}_{ambn} \widehat{R}^{bras} \widehat{R}_{csdr} \widehat{R}^{dncm}\right]\\
& - \frac{1}{2}\left[ R_{mnrs} R^{rsnp} R_{pquv} R^{qmuv}
 + 4 \widehat{R}_{mban} \widehat{R}^{anbp} R_{pquv} R^{qmuv} \right]\\
& - \frac{1}{4} R_{mnrs} R^{rs}{}_{pq} R^{qmuv} R^{np}{}_{uv}\\
& + \frac{1}{16} R_{mnrs} R^{mnpq} R_{pquv} R^{uvrs}\\
& + \frac{1}{32}(R_{rstu} R^{rstu})
\left[R_{mnrs} R^{mnrs}+ 8 \widehat{R}_{ambn} \widehat{R}^{ambn}\right]+ O(\text{5-pt})
\end{aligned}
\label{eq:4pt-gravity-axiodilaton-12d-replaced}
\end{equation}

In this expression we have grouped terms with the same index contraction structure together. 
We again see contraction patterns that could reveal a 12d covariant structure.
For example
\begin{equation}
\widehat{R}_{MNRS}\widehat{R}^{MNRS} = R_{mrns} R^{mnrs} + 4 \widehat{R}_{ambn} \widehat{R}^{ambn} + O(P^3),
\end{equation}
the factor of 4 arises from the 4 ways to choose two torus legs in $\widehat{R}_{MNRS}$ that contribute to 4-pt amplitudes.
Hence the last term in \eqref{eq:4pt-gravity-axiodilaton-12d-replaced} is compatible with arising a 12d contraction $\frac{1}{32} (R_{MNRS} R^{MNRS})^2  \in t_8 t_8 \widehat{R}^4$.
Upon further investigation, one finds
\begin{equation}
\begin{aligned}
\widehat{R}_{PNQM} \widehat{R}^{PRQS} \widehat{R}^{MT}{}_{RU} \widehat{R}^{NU}{}_{ST}
&=
R_{pnqm} R^{prqs} R^{mt}{}_{ru} R^{nu}{}_{st}
+ 2 \widehat{R}_{anbm} \widehat{R}^{arbs} R^{mt}{}_{ru} R^{nu}{}_{st}+ \ldots\\
\widehat{R}_{MPNQ} \widehat{R}^{QRPS} \widehat{R}_{TSUR} \widehat{R}^{UNTM}
&= R_{mpnq} R^{qrps} R_{tsur} R^{untm}
+ 4 \widehat{R}_{ambn} \widehat{R}^{bras} R_{tsur} R^{untm}
+ 2 \widehat{R}_{ambn} \widehat{R}^{bras} \widehat{R}_{csdr} \widehat{R}^{dncm}+ \ldots\\
\widehat{R}_{MNRS} \widehat{R}^{RSNP} \widehat{R}_{PQUV} \widehat{R}^{QMUV}
&= R_{mnrs} R^{rsnp} R_{pquv} R^{qmuv}
 + 4 \widehat{R}_{mban} \widehat{R}^{anbp} R_{pquv} R^{qmuv}+ \ldots\\
\widehat{R}_{MNRS} \widehat{R}^{RS}{}_{PQ} \widehat{R}^{QMUV} \widehat{R}^{NP}{}_{UV}
&= R_{mnrs} R^{rs}{}_{pq} R^{qmuv} R^{np}{}_{uv}+ \ldots\\
\widehat{R}_{MNRS} \widehat{R}^{MNPQ} \widehat{R}_{PQUV} \widehat{R}^{UVRS}
&= R_{mnrs} R^{mnpq} R_{pquv} R^{uvrs}+ \ldots\\
(\widehat{R}_{MNRS}\widehat{R}^{MNRS})^2
&= (R_{rstu} R^{rstu})
\left[R_{mnrs} R^{mnrs}+ 8 \widehat{R}_{ambn} \widehat{R}^{ambn}\right]+ \ldots
\end{aligned}
\end{equation}
where the ellipses denote terms with more than 4 fields in 10d, or terms that vanish when summed with the coefficients in \eqref{eq:t8t8R4}.
Thus, every term in \eqref{eq:4pt-gravity-axiodilaton-12d-replaced} has a origin from a 12d contraction $t_8 t_8 \widehat{R}^4$, upon substituting the specific F-theory ansatze \eqref{eq:F-theory-ansatze}.

The relation above was first noted in \cite{Minasian:2015bxa} in a ``top-down" fashion, by making an informed guess of a 12d effective action, then showing that the resulting 10d action matches the known gravity and axio-dilaton amplitudes.
The ``bottom-up" approach outlined here, despite requires more exercises in index-relabeling and tensor identities, is perhaps more systematic, as it does not require one to make a 12d effective ansatze a priori.
If there were to exist a 12d covariant expression that reproduce any 10d effective action, then after substituting 10d objects for 12d ones, one must be able to find that the terms group into a more natural pattern arising from splitting 12d indices.
Whether one is capable of identifying such a pattern, especially when studying more complicated effective actions, is a separate matter.
But in principle, it can be done\footnote{
    At the moment, there does not exist computer algebra systems that allows one to invert the index-splitting of tensor contractions.
    However, emerging language models have shown capabilities to perform symbolic manipulations that are beyond mechanical, which may be useful for this purpose in the future. 
}.
What would be a genuine obstruction to a 12d covariant interpretation, is if certain terms can not be written using covariant 12d objects at all.

\section{Type IIB at 5 points}

Recently, the 5-point 8-derivative effective action in the axio-dilaton sector has been computed \cite{Liu:2025uqu}.
Interestingly, in the U(1)-preserving sector at 5 points, there exists a term, which realises SL(2, Z)-invariance on its own, with the form (we drop all numerical factors)
\begin{equation}
L_{\text{5pt},\tau} \supset
\text{Re} R^{mnsr} \nabla_m \overline{P}_s \nabla_n \overline{P}_r P_q P^q.
\label{eq:12d-obstruction}
\end{equation}
Both $R^{mnsr}$ and $\nabla_m \overline{P}_s$ can be written as 12d covariant objects (see \eqref{eq:12d-Riemann-complex}).
However, while we may write $P_q \overline{P}^q$ using $\widehat{R}_{z\overline{z}z\overline{z}}$, there is no 12d covariant object that can be substituted for $P_q P^q$.
We now study this term more carefully.

We had previously worked with, from \eqref{eq:12d-Riemann-complex}, the 12d Riemann tensor components for the complex tangent frame coordinates $\widehat{g}_{zz} = \widehat{g}_{\overline{z}\overline{z}} = 0$, $\widehat{g}_{z\overline{z}} = 1/2$. Using real coordinates where $\widehat{g}_{ab} = \frac{1}{\tau_2}\begin{pmatrix}
1 & \tau_1 \\
\tau_1 & |\tau|^2
\end{pmatrix}$, we find the following components of the 12d Riemann tensor

\medskip
\renewcommand{\arraystretch}{1.8}
\begin{tabular}{c|cccccc}
\toprule
$\widehat{R}_{ambn}$ 
  & $\nabla_m\nabla_n\tau_1$ 
  & $\nabla_m\nabla_n\tau_2$ 
  & $(\nabla_m\tau_1)(\nabla_n\tau_1)$ 
  & $(\nabla_m\tau_2)(\nabla_n\tau_2)$ 
  & $\nabla_m\tau_1\nabla_n\tau_2$ 
  & $\nabla_m\tau_2\nabla_n\tau_1$ \\
\midrule
$\widehat{R}_{1m1n}$ & $0$ & $\frac{1}{2\tau_2^2}$ & $\frac{1}{4\tau_2^3}$ & $-\frac{3}{4\tau_2^3}$ & $0$ & $0$ \\
$\widehat{R}_{1m2n}$ & $-\frac{1}{2\tau_2}$ & $\frac{\tau_1}{2\tau_2^2}$ & $\frac{\tau_1}{4\tau_2^3}$ & $-\frac{3\tau_1}{4\tau_2^3}$ & $\frac{1}{4\tau_2^2}$ & $\frac{3}{4\tau_2^2}$ \\
$\widehat{R}_{2m1n}$ & $-\frac{1}{2\tau_2}$ & $\frac{\tau_1}{2\tau_2^2}$ & $\frac{\tau_1}{4\tau_2^3}$ & $-\frac{3\tau_1}{4\tau_2^3}$ & $\frac{3}{4\tau_2^2}$ & $\frac{1}{4\tau_2^2}$ \\

$\widehat{R}_{2m2n}$ & $-\frac{\tau_1}{\tau_2}$ & $\frac{\tau_1^2-\tau_2^2}{2\tau_2^2}$ & $\frac{\tau_1^2-3\tau_2^2}{4\tau_2^3}$ & $\frac{\tau_2^2-3\tau_1^2}{4\tau_2^3}$ & $\frac{\tau_1}{\tau_2^2}$ & $\frac{\tau_1}{\tau_2^2}$ \\
\bottomrule
\end{tabular}
\medskip

As for the rest of the non-vanishing Riemann tensor components,
\begin{equation}
\begin{aligned}
\widehat{R}_{mnab} 
&= 2\widehat{R}_{[a|m|b]n}\\
% = \frac{1}{2\tau_2^2}[\nabla_m\tau_2\nabla_n\tau_1-\nabla_m\tau_1\nabla_n\tau_2],\\
\widehat{R}_{1212}
&= -\frac{1}{2}g^{mn}g^{ab} \widehat{R}_{ambn} 
% = \frac{1}{4\tau_2^2}|\nabla \tau|^2.
\end{aligned}
\end{equation}

Generically $\widehat{R}_{ambn}$, $\widehat{R}_{abcd}$ and $\widehat{R}_{mnab}$ form independent bases for second order derivatives \footnote{We use second order derivative to mean second derivative or products of first derivatives.} of the metric components.
However, for the specific 12d ansatze required by type IIB, $\widehat{R}_{mnab}$ and $\widehat{R}_{abcd}$ can both be obtained as linear combinations or contractions of $\widehat{R}_{ambn}$.
A direct consequence of such lack of independent Riemann tensor components is that there may be second order derivatives of $\tau$ that the 12d Riemann tensor can not capture.
For example, while we can construct $(\nabla \tau_1)^2 + (\nabla \tau_2)^2$ using $\widehat{R}_{1212}$, we can not construct $(\nabla \tau_1)^2 - (\nabla \tau_2)^2$
or $\nabla_m \tau_1 \nabla_n \tau_2$
\footnote{
    Since all nonvanishing 12d Riemann tensors are either pure 10d Riemann tensors or can be obtained via $\widehat{R}_{ambn}$, it suffices to consider linear combinations of $\widehat{R}_{ambn}$, i.e. our table. Demanding no appearances of $\nabla^2 \tau_1$ or $\nabla^2 \tau_2$ enforces $(\nabla \tau_1)^2$ to appear with the same sign as $(\nabla \tau_2)^2$, and that the cross-term $\nabla_m \tau_1 \nabla^m \tau_2$ vanishes.
}
.
Given that
\begin{equation}
P_m P^m = -\frac{1}{4\tau_2^2} 
\left[
    (\nabla\tau_1)^2 - (\nabla\tau_2)^2 + 2i \nabla^m \tau_1 \nabla_m \tau_2
\right],
\end{equation}
the contribution from \eqref{eq:12d-obstruction}, which realizes SL(2, Z) on its own, can not be written in a 12d covariant manner.
We note that the rest of the terms in the U(1)-preseving 5-point effective action in \cite{Liu:2025uqu} do not suffer from this problem.
It was already noted in \cite{Liu:2025uqu} that at 5-pt in the U(1)-preserving sector, certain axio-dilaton couplings begin to deviate from those predicted by $t_8t_8 \widehat{R}^4$.
Our result here is stronger as we have shown that no covariant contraction of any type in 12d, may capture the 5-pt dynamics of type IIB.

\section{Discussion}
We have argued that the answer to whether type IIB effective actions have 12d interpretations is subtle.
While at 4 pts the answer is yes, at 5 pt there exists fundamental obstructions, and this does not have to do with U(1)-violation.
Indeed, it is possible, that beginning at 6-pt or above, there appears additional 12d obstructive terms, similar to the $PP$ described here that together with the 5-pt terms, somehow conspire to support 12d covariant uplift.
To investigate this possibility, one needs axio-dilaton effective actions up to 8 points.
The alternative is that the obstruction we found is real, and type IIB effective actions can not be written in 12d covariant form.


% We will now discuss 12d perspectives on the type IIB effective action, and argue that type IIB effective actions can not be written in 12d covariant form.
% This is separate from the arguments related to the Eisenstein series structure, as well as the U(1)-violating sector, which has been recognized as difficult to be understood from 12d perspective \cite{Minasian:2015bxa,Liu:2025uqu}.
% However, nevertheless, one may still hope that 12d contractions, upon reduction to 10d, and after applying LSZ reduction, produce the kinematic structure of string scattering amplitudes.
% We argue that this can not be done.



% A general strategy for uplifting type IIB effective action may look like the following. Examine the effective action, substituting $\tau_1, \tau_2$ for components of the 12d metric on $T_2$, and derivatives of $\tau_1, \tau_2$ for 12d Riemannt tensor.
% This packages SL(2, Z) as part of 12d covariance. 
% One may then examine whether the resulting expression, in particular the coefficient of the distinct contraction patterns, may have a natural interpretation as arising from a higher dimensional contraction.
% The idea is that if certain terms of the 10d effective action arises from a 12d contraction, then one must be able to rewrite the 10d effective action to invert the index splitting, and promote a group of 10d terms to a 12d contraction.


% We note that crucially, while for a generic 12d metric ansatze, $R_{ambn}, R_{mnab}, R_{abcd}$ are independent of each other, for the specific F-theory ansatze, $R_{mnab}$ and $R_{abcd}$ can both be obtained as linear combinations or contractions of $R_{ambn}$.
% For example, $R_{z\overline{z}z\overline{z}} = \tfrac12 R^m{}_{zm\overline{z}}$, and $R_{mnz\overline{z}} = R_{m\overline{z}nz} - R_{mzn\overline{z}}$, leaving us with only 4 linearly independent components.
% This basis mismatch is related to the specific 12d metric ansatze chosen, and has important consequences as we will see.

