\section{IIA and 11d}

Although F1 and NS5 are often called the ``electric'' and ``magnetic'' branes in type IIA, they are not electromagnetic duals of each other in 10d, as one can quickly verify\footnote{We have provided the brane solutions in section \ref{sec:10d IIA branes} for reference.}.
The obstruction is not merely a matter of naming conventions\footnote{The electric ansatz places the form potential along the worldvolume, while the magnetic ansatz has the flux along the transverse directions; see \cite{Stelle:1998xg}.}: even after swapping the $H_3$ configuration of NS5 into that of F1, the Einstein equation is not satisfied unless one also performs the exchange $e^{\Phi} \to e^{-\Phi}$ to support the NS5 metric.
Since the dilaton is does not transform under EM duality, this suggests a nontrivial relation between the dilaton and electromagnetic duality, as can already be seen from the general $p$-brane formulation \cite{Stelle:1998xg}, which we summarize in section \ref{sec:general brane solns}.

The dilaton is often understood as the modulus of a compact higher dimension.
We would like to ask whether the EM duality may be understood from the higher dimension, where the lower-dimensional dilaton, now part of the metric, participates in the EM duality.
In 11d supergravity, we have the M2 brane \ref{sec:11d branes} obtained using the electric ansatz \ref{sec:general brane solns}
\begin{equation}
ds^2_{M2} = H^{-2/3}ds_{1,2}^2 + H^{1/3}ds_8^2,\quad
(F_4)_{\mu_0 \mu_1 \mu_2 m} = \varepsilon_{\mu_0 \mu_1 \mu_2}\partial_m(H^{-1})
\label{M2-brane}
\end{equation}
In the action containing $F_4 = dC_3$, there is an equivalent formulation using the dual field strength 
\begin{equation}
F_7 = (i)^{[t]}*_{11} F_4.
\end{equation}
We can apply the electric ansatz to $F_7$ instead, obtaining another spacetime, where the dual field $F_7$ propagates
\begin{equation}
ds^2_{\text{5-brane}} = H^{-1/3}ds_{1,5}^2 + H^{2/3}ds_5^2,\quad
(F_7)_{\mu_0 ... \mu_5 m} = \varepsilon_{\mu_0 ... \mu_5}\partial_m(H^{-1})
\label{M2-brane dual}
\end{equation}
To obtain the form field configuration in terms of $F_4$, we perform EM duality on $F_7$, since $F_7$ is defined within the 5-brane spacetime, we should use the metric of the 5-brane to perform the Hodge star, doing so we indeed recover what's commonly known as the M5 brane solution
\begin{equation}
ds^2_{M5} = H^{-1/3}ds_{1,5}^2 + H^{2/3}ds_5^2,\quad
(F_4)_{m_1 m_2 m_3 m_4} = \varepsilon_{m_1 m_2 m_3 m_4 n} \partial_n H.
\label{M5-brane}
\end{equation}
In 11 dimensions, the M2 and M5 can indeed be claimed to be dual to each other: the M5 spacetime is indeed a dual spacetime supported by the dual field strength $F_7$.

Upon reduction to 10d type IIA, the F1 and NS5 branes are obtained from compactifying M2 and M5, in this inheritence the EM duality relation may be understood.
But in 10d alone, the names ``electric" and ``magnetic" branes should be taken with caution: there is no true duality relation between F1, NS5, or between D2 and D4. The only exception being the D3 brane in type IIB, where the dilaton is constant and the field strength $F_5$ is self-dual.

\paragraph{Side note}
Somewhat unrelated but interesting, in \eqref{M2-brane}, \eqref{M2-brane dual}, and \eqref{M5-brane} we have written the form fields with flat $\varepsilon$ symbols, and the contraction is done with $\delta_{mn}$ in \eqref{M5-brane}.
This is also the standard way to present these solutions in the literature.
They can also be rewritten with the curved space $\epsilon$ tensors, and the contraction done with the curved metric.
As in, we can write \eqref{M2-brane} as
\begin{equation}
(F_4)_{\mu_0 \mu_1 \mu_2 m} = \epsilon_{\mu_0 \mu_1 \mu_2}\partial_m \ln H,
\end{equation}
\eqref{M2-brane dual} as
\begin{equation}
(F_7)_{\mu_0 ... \mu_5 m} = \epsilon_{\mu_0 ... \mu_5}\partial_m \ln H,
\end{equation}
and \eqref{M5-brane} as
\begin{equation}
(F_4)_{m_1 m_2 m_3 m_4} = \epsilon_{m_1 m_2 m_3 m_4 n}g^{np} \partial_p \ln H.
\end{equation}

% TODO: elucidate the inverse dilaton profile between F1 and NS5, and relate that to 11d duality. The fact that the circle felt by F1 is inverse to the circle feld by NS5 may have a clean explanation from 11d duality combined with wrapping on the circle.

\section{IIB and 12d}

We would like to ask the same question about type IIB.
Despite one often think of F1 and NS5, D1 and D5 as EM dual pairs, their form fields $H_3$ AND $F_3$ configuration are not related by EM duality, in 10d, and of course they have opposite dilaton profiles as well\footnote{The brane solutions are listed in \ref{sec:10d IIB branes}}.

To obtain the NS5 from F1 by EM duality, one actually has to perform an accompanying SL(2, Z) transformation to invert the dilaton.
Similar situation is encountered on the D3 brane worldvolume \cite{Tseytlin:1996it}.
Recently a 12d uplift of the various form fields have been proposed \cite{Cheng:2025efp}. Let us uplift the F1, D1, NS5, D5 branes to 12d.

\paragraph{F1}
\begin{align}
ds^2
&= H^{-3/4}ds_{1,1}^2 
+ H^{1/4}ds_8^2
+H^{-1/2}dz_1^2
+H^{1/2}dz_2^2\\
(\mathcal{F}_4)_{\mu_0 \mu_1 m z_1} 
&= \varepsilon_{\mu_0 \mu_1}\partial_m H^{-1}
\end{align}

\paragraph{D1}
\begin{align}
ds^2
&= H^{-3/4}ds_{1,1}^2 
+ H^{1/4}ds_8^2
+H^{1/2}dz_1^2
+H^{-1/2}dz_2^2\\
(\mathcal{F}_4)_{\mu_0 \mu_1 m z_2} 
&= \varepsilon_{\mu_0 \mu_1}\partial_m H^{-1}
\end{align}


\paragraph{NS5}
\begin{align}
ds^2
&= H^{-1/4}ds_{1,5}^2 
+ H^{3/4}ds_4^2
+H^{1/2}dz_1^2
+H^{-1/2}dz_2^2\\
(\mathcal{F}_4)_{m_1 m_2 m_3 z_1} 
&= \varepsilon_{m_1 m_2 m_3 m}\partial_m H
\end{align}

\paragraph{D5}
\begin{align}
ds^2
&= H^{-1/4}ds_{1,5}^2 
+ H^{3/4}ds_4^2
+H^{-1/2}dz_1^2
+H^{1/2}dz_2^2\\
(\mathcal{F}_4)_{m_1 m_2 m_3 z_2} 
&= \varepsilon_{m_1 m_2 m_3 m}\partial_m H
\end{align}

In 12d the SL(2, Z) transformation $e^\Phi \to e^{-\Phi}$ becomes $z_1 \to z_2, z_2 \to -z_1$, which indeed maps between the F1 and D1 and between the NS5 and D5 solutions.

There is a pattern here: the F1 uplift's form field configurations and that of the D5 uplift are very close to being related by EM duality in 12d, and so are the D1 and NS5 uplifts.

Let us perform EM duality on the $\mathcal{F}_4$ configuration of F1.
\begin{equation}
(\mathcal{F}_8)_{m_1 m_2 ...m_7 z_2} = \varepsilon_{m_1 m_2 m_3 ... m_7 n}\partial_n H
\end{equation}
if we decompose $\mathcal{F}_8$ back to $\mathcal{F}_4$ in 12d, by $\mathcal{F}_8 = \varepsilon_4 \wedge \mathcal{F}_4$, this is indeed the $\mathcal{F}_4$ configuration of the D5 uplift. From there performing SL(2, Z) duality $z_1 \leftrightarrow z_2$ we reach the NS5 uplift.

\subsection{Speculative work: Attempt to deriving the D1,F1,NS5,D5 uplifts in 12d}

We will now follow a similar line of reasoning as has been carried out for the type IIA/11d case in the previous chapter, and steps to derive brane solutions in \cite{Stelle:1998xg}.
We will derive a class of solutions for the Einstein equation supported by a form field.
Consider the following action in $D$ dimensions
\begin{equation}
2\kappa_D^2 S = \int d^D x \sqrt{-g}\left(R - \frac{1}{2}|F_n|^2\right).
\end{equation}
For the following metric ansatz
\begin{equation}
ds^2 = e^A ds_{d}^2 + e^B ds_{D-d-2}^2 + e^C dz_1^2 + e^{-C} dz_2^2,
\end{equation}
and assuming the functions only depend on $x^m$.
One can show that letting the coordinates be $(x^{\mu}, y^m, z_1, z_2)$ with $\mu = 0,...,d-1$ and $m = 1,...,D-d-2$.
Assuming that $e^A = H^a, e^B = H^b, e^C = H^c$ for some harmonic function $H$, and that the form field ansatz is that $F_n \sim dH$ which satisfies the Bianchi identity,
the Ricci tensor components are \footnote{see Appendix \ref{sec:ricci tensor with isometries}}
\begin{align}
R_{\mu\nu}
&=\frac{a}{2}\eta_{\mu\nu}H^{a-b-2}(H')^2\\
R_{zz}
&=\pm\frac{c}{2}H^{-b\pm c-2}(H')^2\\
R_{mn}
&=H^{-2}(H')^2\left[\frac{b}{2}\delta_{mn} + \left(\frac{da(b-a)}{4} - \frac{c^2}{2}\right)\frac{y^m y^n}{r^2}\right]
\end{align}
For an ansatz we let the potential along the $d$-dimensional worldvolume as well as one of the $z$ directions, i.e.
\begin{equation}
(F_n)_{\mu_0...\mu_{d-1} m z_1} = \varepsilon_{\mu_0...\mu_{d-1}}H^f \partial_m H
\end{equation}
for some $f$.
Then we find
\begin{align}
|F_n|^2 &= (-1)^{[t]}H^{2f-ad-b-c}(H')^2\\
|FF|_{\mu\nu}&=
(-1)^{[t]}\eta_{\mu\nu} H^{2f-b-a(d-1)-c}(H')^2\\
|FF|_{z_1z_1}&=(-1)^{[t]}H^{2f-ad-b}(H')^2\\
|FF|_{mn}&=(-1)^{[t]}H^{2f-ad-c}\partial_m H \partial_n H
\end{align}
we can compute
\begin{align}
S_{\mu\nu}
&=\frac{1}{2}(-1)^{[t]}\eta_{\mu\nu}(H')^2 H^{2f-b-a(d-1)-c}\left(\frac{D-n-1}{D-2}\right)\\
S_{z_1 z_1}
&=(-1)^{[t]}\frac{1}{2}H^{2f-ad-b}(H')^2\left[1-\frac{n-1}{D-2}\right]\\
S_{z_2 z_2}
&=(-1)^{[t]}\frac{1}{2}H^{2f-ad-b-2c}(H')^2\left[-\frac{n-1}{D-2}\right]\\
S_{mn}
&=(-1)^{[t]}\frac{1}{2}H^{2f-ad-c}
\left[
    \partial_m H\partial_n H - \frac{n-1}{D-2}\delta_{mn}(H')^2
\right]
\end{align}
From the Einstein equation $R_{MN} = S_{MN}$, we can match the powers of $H$ to obtain
\begin{equation}
2f - ad - c = -2
\end{equation}
the ansatz implies
\begin{equation}
n=d+2
\end{equation}
and the $R_{zz}$ equation gives
\begin{equation}
n = D/2
\end{equation}
Finally, we are left with
\begin{align}
a&=(-1)^{[t]}\left(\frac{D-n-1}{D-2}\right)\\
c&=(-1)^{[t]}\left(\frac{D-n-1}{D-2}\right)\\
b&=(-1)^{[t]}\left(-\frac{n-1}{D-2}\right)\\
(-1)^{[t]}&=
\frac{da(b-a)}{2} - c^2
\end{align}
This system has a unique solution $(-1)^{[t]} = -1$, $D=10$, $n=5$, $d=3$, $f=-2$ with $a=c=-1/2, b=1/2$.
We find ourselves with the 3-brane wrapped on one-cycle of the torus.
\begin{align}
ds_{10}^2 &= H^{-1/2}[ds_{1,2}^2 + dz_1^2] + H^{1/2}[ds_5^2 + dz_2^2]\\
(F_5)_{\mu_0 \mu_1 \mu_2 m z_1} &= \varepsilon_{\mu_0 \mu_1 \mu_2}\partial_m (H^{-1})
\end{align}
It has a dual spacetime where a dual $\tilde F_5 \equiv (i) *F_5$ propagates, with the same metric
\begin{align}
ds_{10}^2 &= H^{-1/2}[ds_{1,2}^2 + dz_1^2] + H^{1/2}[ds_5^2 + dz_2^2]\\
(\tilde F_5)_{\mu_0 \mu_1 \mu_2 m z_1} &= \varepsilon_{\mu_0 \mu_1 \mu_2}\partial_m (H^{-1})
\end{align}
which corresponds to a configuration of $F_5$ given by
\begin{align}
F_5 &= (-1)^{[t]}(-i)*\tilde F_5\\
(F_5)_{m_1 m_2 m_3 m_4 z_2}&=i\varepsilon_{m_1m_2m_3 m_4 n} \partial_n H
\end{align}

Comments: This does not make much sense, I started out looking for a solution in 12d, but ended up with a unique solution in 10d... So far I have not been able to catch a mistake. 

